### 2017-02-03 manuscript.rmd
touched up overview figure, generate expectation figure with code

![Figure Expectations](figure_expectations.png?raw=true)

@@

@@

	# Replace the actual Tau values with simulated Tau values, using parameters 
	# fitted from each tree
	gene_trees_sim_null = lapply( gene_trees_calibrated[1:1000], sim_tau )

@@

	# Replace the actual Tau values with simulated Tau values, using parameters 
	# fitted from each tree. 
	gene_trees_sim_oc = lapply( gene_trees_calibrated[1:1000], sim_tau, dup_adjust=dup_adjust )

@@

	g_phylo_null = 
		nodes_sim_null_contrast %>% 
		ggplot( aes( x=pic, y=..density.., col=Event ) ) + 
			geom_freqpoly( binwidth=.001, position="identity" ) +
			xlab( "Phylogenetic Independent Contrast" ) +
			ylab( "Density" ) +
			xlim( 0, 0.05 ) + 
			ylim( 0, 75 ) +
			theme_classic() + 
			ggtitle( "(b) Null simulation, phylogenetic" ) +
			theme(legend.justification=c(1,1), legend.position=c(1,1))

	g_pair_null = 
		pairwise_sim_null_summary %>% 
		filter( species_a == "homo_sapiens" | species_b == "homo_sapiens" ) %>% 
		filter( ! is.na( D ) ) %>%
		group_by( Event, label ) %>% 
		summarise( cor.test(  tau_a, tau_b )$estimate, n=n() ) %>% 
		rename( rho=`cor.test(tau_a, tau_b)$estimate` ) %>%
		rename( clade = label ) %>% 
		left_join( calibration_times, clade=clade ) %>%
		ggplot() + 
			geom_point( aes( x=age, y=rho, col=Event, size=n ) ) +
			theme_classic() +
			xlab( "Age" ) +
			ylab( "Rho" ) +
			ggtitle( "(a) Null simulation, pairwise" ) +
			theme(legend.position="none")

	g_phylo_oc = 
	nodes_sim_oc_contrast %>% 
	ggplot( aes( x=pic, y=..density.., col=Event ) ) + 
		geom_freqpoly( binwidth=.001, position="identity" ) +
		xlab( "Phylogenetic Independent Contrast" ) +
		ylab( "Density" ) +
		xlim( 0, 0.05 ) + 
		ylim( 0, 75 ) +
		theme_classic() + 
		ggtitle( "(d) OC simulation, phylogenetic" ) +
		theme(legend.position="none")

	g_pair_oc = 
		pairwise_sim_oc_summary %>% 
		filter( species_a == "homo_sapiens" | species_b == "homo_sapiens" ) %>% 
		filter( ! is.na( D ) ) %>%
		group_by( Event, label ) %>% 
		summarise( cor.test(  tau_a, tau_b )$estimate, n=n() ) %>% 
		rename( rho=`cor.test(tau_a, tau_b)$estimate` ) %>%
		rename( clade = label ) %>% 
		left_join( calibration_times, clade=clade ) %>%
		ggplot() + 
			geom_point( aes( x=age, y=rho, col=Event, size=n ) ) +
			theme_classic() +
			xlab( "Age" ) +
			ylab( "Rho" ) +
			ggtitle( "(c) OC simulation, pairwise" ) +
			theme(legend.position="none")

@@

>>>>

@@

```{r expectation_plots, echo=FALSE, cache=TRUE, message=F, warning=F}

	sim_expectation = function( scale = 1, n = 10000 ){
		expectation = 
			bind_rows(
				data.frame( 
					pic = rgamma( n, 1, scale = scale ),
					Event = "Duplication",
					stringsAsFactors = FALSE
				),
				data.frame( 
					pic = rgamma( n, 1, scale = 1 ),
					Event = "Speciation",
					stringsAsFactors = FALSE
				)
			)

		event_levels = c( "Speciation", "Duplication" )
		expectation$Event = 
			factor( expectation$Event, levels=event_levels )

		return( expectation )
	}

	g_expectation_null =
		sim_expectation() %>%
		ggplot( aes( x=pic, y=..density.., col=Event ) ) + 
			geom_freqpoly(  binwidth=0.2, position="identity" ) +
			xlab( "Phylogenetic independent contrasts (PIC)" ) +
			ylab( "Density" ) +
			xlim( 0, 6 ) + 
			theme_classic() +
			theme( 
				axis.text.x=element_blank(), 
				axis.ticks.x=element_blank(), 
				axis.text.y=element_blank(), 
				axis.ticks.y=element_blank(),
				legend.justification=c( 1, 1 ), 
				legend.position=c( 1, 1 )
			) +
			ggtitle( "(a) Null expectation" )

	g_expectation_oc =
		sim_expectation( scale=2 ) %>%
		ggplot( aes( x=pic, y=..density.., col=Event ) ) + 
			geom_freqpoly(  binwidth=0.2, position="identity" ) +
			xlab( "Phylogenetic independent contrasts (PIC)" ) +
			ylab( "Density" ) +
			xlim( 0, 6 ) + 
			theme_classic() +
			theme( 
				axis.text.x=element_blank(), 
				axis.ticks.x=element_blank(), 
				axis.text.y=element_blank(), 
				axis.ticks.y=element_blank(),
				legend.position="none"
			) +
			ggtitle( "(b) Ortholog Conjecture (OC) expectation" )

	grid.arrange(
			g_expectation_null,
			g_expectation_oc,
			ncol = 2
		)

@@

	# Replace the actual Tau values with simulated Tau values, using parameters 
	# fitted from each tree
	gene_trees_sim_null = lapply( gene_trees_calibrated, sim_tau )

@@

	# Replace the actual Tau values with simulated Tau values, using parameters 
	# fitted from each tree. 
	gene_trees_sim_oc = lapply( gene_trees_calibrated, sim_tau, dup_adjust=dup_adjust )

@@

	g_phylo_null = 
		nodes_sim_null_contrast %>% 
		ggplot( aes( x=pic, y=..density.., col=Event ) ) + 
			geom_freqpoly( binwidth=.0025, position="identity" ) +
			xlab( "Phylogenetic Independent Contrast" ) +
			ylab( "Density" ) +
			xlim( 0, 0.05 ) + 
			ylim( 0, 75 ) +
			theme_classic() + 
			ggtitle( "(b) Null simulation, phylogenetic" ) +
			theme( legend.justification=c( 1, 1 ), legend.position=c( 1, 1 ) )

	g_pair_null = 
		pairwise_sim_null_summary %>% 
		filter( species_a == "homo_sapiens" | species_b == "homo_sapiens" ) %>% 
		filter( ! is.na( D ) ) %>%
		group_by( Event, label ) %>% 
		summarise( cor.test(  tau_a, tau_b )$estimate, n=n() ) %>% 
		rename( rho=`cor.test(tau_a, tau_b)$estimate` ) %>%
		rename( clade = label ) %>% 
		left_join( calibration_times, clade=clade ) %>%
		ggplot() + 
			geom_point( aes( x=age, y=rho, col=Event, size=n ) ) +
			theme_classic() +
			xlab( "Age" ) +
			ylab( "Rho" ) +
			ylim( 0, 1 ) +
			ggtitle( "(a) Null simulation, pairwise" ) +
			theme(legend.position="none")

	g_phylo_oc = 
	nodes_sim_oc_contrast %>% 
	ggplot( aes( x=pic, y=..density.., col=Event ) ) + 
		geom_freqpoly( binwidth=.0025, position="identity" ) +
		xlab( "Phylogenetic Independent Contrast" ) +
		ylab( "Density" ) +
		xlim( 0, 0.05 ) + 
		ylim( 0, 75 ) +
		theme_classic() + 
		ggtitle( "(d) OC simulation, phylogenetic" ) +
		theme(legend.position="none")

	g_pair_oc = 
		pairwise_sim_oc_summary %>% 
		filter( species_a == "homo_sapiens" | species_b == "homo_sapiens" ) %>% 
		filter( ! is.na( D ) ) %>%
		group_by( Event, label ) %>% 
		summarise( cor.test(  tau_a, tau_b )$estimate, n=n() ) %>% 
		rename( rho=`cor.test(tau_a, tau_b)$estimate` ) %>%
		rename( clade = label ) %>% 
		left_join( calibration_times, clade=clade ) %>%
		ggplot() + 
			geom_point( aes( x=age, y=rho, col=Event, size=n ) ) +
			theme_classic() +
			xlab( "Age" ) +
			ylab( "Rho" ) +
			ylim( 0, 1 ) +
			ggtitle( "(c) OC simulation, pairwise" ) +
			theme(legend.position="none")

@@

### Software versions

This manuscript was computed on `r format( Sys.time(), "%a %b %d %X %Y" )` with the following R package versions.

```{r session_summary, echo=FALSE, comment=NA}
	sessionInfo()
```
